Structural Breaks in Inflation Dynamics within the European Monetary Union

### 2011-03-11 pkg/paper/Paper/draft.Rnw
updated results, draft and papers.bib
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/glogis@77 b679b2f7-6539-45d0-a605-5ddcb976cde9

## For the creation of the tables
## <<tabelle, eval=FALSE>>=
root_dir <- do.call("file.path", as.list(head(strsplit(getwd(), .Platform$file.sep)[[1]], -1)))
if(!file.exists(file.path(root_dir, "Analysis", "Austria.rda"))) {
setwd(file.path(root_dir, "Analysis"))
Sweave("results.Rnw")
setwd(file.path(root_dir, "Draft"))
}
## query result file names
fnam <- Sys.glob(file.path("..", "Analysis", "*.rda"))
fnam2 <- grep("2", fnam, fixed = TRUE)
if(length(fnam2) > 0) fnam <- fnam[-fnam2]

@@

## to change to shorter names if necessary
names(HICP) <- c("Austria",  "Belgium", "CzechRepublic", "Denmark", "Estonia", 
"Finland", "France",  "Germany", "Greece", "Hungary", "Ireland",  "Italy", "Luxembourg", "Netherlands",
"Poland", "Portugal",  "Slovakia", "Slovenia",  "Spain", "Sweden", "UK")
@
%
%% analysis "macro" (assumes existence of "i", "HICP", and "add_breaks")
<<analysis, eval=FALSE>>=
## compute returns
x <- 100 * diff(log(na.omit(HICP[,i])))

## fit full-sample model
x_gf <- glogisfit(x)

## assess stability of full-sample model
x_efp <- gefp(x_gf, fit = NULL)

## estimate breakpoints (with minimal segment size of 2 years)
x_bp <- breakpoints(x_gf, h = 24)

## (minimal) number of breaks
x_nbreaks <- if(sctest(x_efp, functional = supLM(0.1))$p.value > 0.05) {
  0
} else {
  max(1, length(breakdates(x_bp))) + add_breaks[i]
}

## refit segmented model
x_rf <- refit(x_bp, breaks = x_nbreaks)

## save everything
save(x, x_gf, x_efp, x_bp, x_nbreaks, x_rf, file = paste(colnames(HICP)[i], ".rda", sep = ""))

## plot "macros" (assuming existence "x", "x_gf", ...)

<<plot3, eval=FALSE>>=
  glmean <- function(x) {
    if(any(is.na(x))) NA else glogisfit(x, hessian = FALSE)$moments[1]
  }
  ## returns
  hicp <- diff(log(HICP[,]))

  ## rolling GL means
  hicp_glmean <- rollapply(hicp, 12, glmean)

  ## semi-transparent gray and red
  gray_red <- rgb(c(0.2, 0.8), c(0.2, 0), c(0.2, 0), alpha = 0.3)

  ## plot returns (gray) and rolling means (red)
  plot(hicp, plot.type = "single", lwd = 1.5, col = gray_red[1], xlab="Time", ylab="Series")
  for(i in 1:ncol(hicp)) lines(hicp_glmean[,i], lwd = 1.5, col = gray_red[2])
@

<<plot4, eval=TRUE>>=
## plot convergence in mean
  glmean <- function(x) {
    if(any(is.na(x))) NA else glogisfit(x, hessian = FALSE)$moments[1]
  }
  ## returns
  hicp <- diff(log(HICP[,]))

  ## rolling GL means
  ## without Estonia,  Slovakia, Slovenia
  hicp_glmean <- rollapply(hicp, 12, glmean)
  hicp_euro <- diff(log(HICP[, c(1,2,6,7,8,9,11,12,13,14,16,19)]))
	mean_euro <- hicp_glmean[, c(1,2,6,7,8,9,11,12,13,14,16,19)]

@@

	plot(diff)
@

@@

%(...some problems with graph creation inside .rnw, hope to fix it later ...) \\
% was i zum sega ket hob ba busetti --> vgl. archivierte Datei vom 16.11
% actually too detailed for so small a picture
% des if un die } for am ät dazuatoa

\begin{figure}[h!tp]
<<greyplot, fig=TRUE, height=8, width=8>>=
##if(!file.exists(file.path(root_dir, "Draft", "draft-greyplot.pdf"))) {
<<plot3>>
##}
@
\caption{Inflation rates and mean inflation rates over time}
\end{figure}

%\begin{figure}[h!tp]
%\includegraphics[width=150mm, height=100mm]{draft-greyplot}
%\caption{Inflation rates and mean inflation rates over time}
%\end{figure}

@@

%\begin{figure}[h!tp]
%\includegraphics[width=150mm, height=100mm]{diffmean}
%\caption{Differences in Euro--are mean without Ireland}
%\end{figure}

\begin{figure}[h!tp]
<<diffmean, fig=TRUE, height=8, width=8>>=
##if(!file.exists(file.path(root_dir, "Draft", "diffmean.pdf"))) {
<<plot4>>
##}
@
\caption{Differences in Euro excluding Estonia, Slovenia and Slovakia}
\end{figure}

>>>>

## For the creation of the tables
## <<tabelle, eval=FALSE>>=
root_dir <- do.call("file.path", as.list(head(strsplit(getwd(), .Platform$file.sep)[[1]], -1)))
if(!file.exists(file.path(root_dir, "Analysis", "Austria.rda"))) {
setwd(file.path(root_dir, "Analysis"))
## run results3 (with dummy creation for sales periods)
Sweave("results3.Rnw")
setwd(file.path(root_dir, "Draft"))
}

## query result file names
fnam <- Sys.glob(file.path("..", "Analysis", "*.rda"))
fnam2 <- grep("2", fnam, fixed = TRUE)
if(length(fnam2) > 0) fnam <- fnam[-fnam2]

@@

## to change to shorter names if necessary
names(HICP) <- c("Austria",  "Belgium", "CzechRepublic", "Denmark", "Estonia", 
"Finland", "France",  "Germany", "Greece", "Hungary", "Ireland",  "Italy", "Luxembourg", "Netherlands",
"Poland", "Portugal",  "Slovakia", "Slovenia",  "Spain", "Sweden", "UK")

## include glmean dataset
if(!file.exists(file.path(root_dir, "Analysis", "glmean.rda"))) {
  glmean <- function(x) {
    if(any(is.na(x))) NA else glogisfit(x, hessian = FALSE)$moments[1]
  }
  ## returns
  hicp <- diff(log(HICP[,]))
  ## rolling GL means

  hicp_glmean <- rollapply(hicp, 12, glmean)

  hicp_euro <- diff(log(HICP[, c(1,2,6,7,8,9,11,12,13,14,16,19)]))
	mean_euro <- hicp_glmean[, c(1,2,6,7,8,9,11,12,13,14,16,19)]

@@

  setwd(file.path(root_dir, "Analysis"))
	save(hicp, hicp_glmean, diff, file = "glmean.rda")
	setwd(file.path(root_dir, "Draft"))

}

@

@@

\begin{figure}[h!tp]
<<greyplot, fig=TRUE, height=8, width=8>>=
  gray_red <- rgb(c(0.2, 0.8), c(0.2, 0), c(0.2, 0), alpha = 0.3)
  ## plot returns (gray) and rolling means (red)
  plot(hicp, plot.type = "single", lwd = 1.5, col = gray_red[1], xlab="Time", ylab="Series")
  for(i in 1:ncol(hicp)) lines(hicp_glmean[,i], lwd = 1.5, col = gray_red[2])
@
\caption{Inflation rates and mean inflation rates over time}
\end{figure}

@@

\begin{figure}[h!tp]
<<diffmean, fig=TRUE, height=8, width=8>>=
	plot(diff)
@
\caption{Differences in Euro excluding Estonia, Slovenia and Slovakia}
\end{figure}
